Figures from: Vertebrate host availability and the thermal properties of mosquito-borne parasite transmission

### 2023-12-07 manuscript-figures.Rmd
remake sensitivity plot
following Mordecai 2013 Fig. 3(a)

# Helper function: apply nice labels for focal variables
focalvar_labeller <- function(df) {
  df <- df %>%
    mutate(focal_var = ifelse(focal_var == "muV", "lf", focal_var)) %>%
    mutate(focal_var = factor(focal_var,
                              levels = c("lf", "sigmaV", "sigmaV_f", "rhoL", "deltaL", "etaV", "betaV"),
                              labels = c(
                                TeX("Adult lifespan"),
                                TeX("Biting frequency"),
                                TeX("Eggs per female per day"),
                                TeX("Immature development rate"),
                                TeX("Prob. of immature survival"),
                                TeX("Prob. of surviving EIP"),
                                TeX("Vector competence")
                              )
    ))
}

@@

dR0dk.df <- data.dR0dvar %>%
  filter(
    KH %in% KH_vals,
    sigmaH %in% c(100, Inf)
  ) %>%
  right_join(select(data.R0, system_label, Temperature, Model, sigmaH, KH, median_R0 = median) %>%
               filter(KH %in% KH_vals & sigmaH %in% c(100, Inf))) %>%
  filter(median_R0 > 0) %>%
  mutate(abs_median = abs(median)) %>%
  mutate(sign_median = sign(median)) %>%
  filter(sign_median != 0, !is.na(sign_median)) %>%
  arrange(sign_median) %>%
  arrange(Temperature)

plot.dR0dk <- dR0dk.df %>%
  # Make a stacked plot, colored by parameter
  ggplot(aes(x = Temperature, y = median, color = focal_var, linetype = (as.factor(sign_median)))) +
  geom_line(lwd = 1) +
  scale_color_manual(
    name = "Focal trait:",
    values = rev(c4a("misc.okabe", 7))
  ) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(
    name = unname(TeX("Local sensitivity of $R_0$")),
    # limits = c(-2,2),
    # limits = 10^c(-4, 3),
    # breaks = 10^(seq(-4, 3)),
    # labels = TeX(c("$10^{-4}$", "$10^{-3}$", "$10^{-2}$", "$10^{-1}$", "$10^0$", "$10^1$", "$10^2$", "$10^3$")),
    # trans = "log10",
    expand = c(0, 0)
  ) +
  scale_linetype_manual(
    name = "Sign of sensitivity:",
    values = c(1, 3),
    breaks = c(1, -1),
    labels = c("Positive", "Negative")
  ) +
  facet_rep_grid(
    cols = vars(system_label),
    rows = vars(KH, sigmaH),
    labeller = labeller(
      system_label = sens_labels,
      sigmaH = as_labeller(appender_sigmaH, default = label_parsed),
      KH = as_labeller(appender_KH, default = label_parsed)
    ),
    scales = "free"
  ) +
  guides(linetype = guide_legend(
    title.position = "left",
    title.vjust = 0.5,
    direction = "vertical"
  )) +
  theme_minimal_hgrid(10) +
  theme(
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 8),
    legend.position = "bottom",
    legend.justification = 0.5,
    axis.title.x = element_text(hjust = 0.5),
    strip.text.x = ggtext::element_markdown(
      size = 10,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  )

>>>>

# Helper function: apply nice labels for focal variables
focalvar_labeller <- function(df) {
  df <- df %>%
    mutate(focal_var = factor(focal_var,
                              levels = c("total", "muV", "sigmaV", "sigmaV_f", "rhoL", "deltaL", "etaV", "betaV"),
                              labels = c(
                                TeX("Overall"),
                                TeX("Adult mortality rate"),
                                TeX("Biting frequency"),
                                TeX("Eggs per female per day"),
                                TeX("Immature development rate"),
                                TeX("Prob. of immature survival"),
                                TeX("Parasite development rate"),
                                TeX("Vector competence")
                              )
    ))
}

@@

temp_lims <- data.dR0dvar %>% 
  filter(focal_var == "Adult mortality rate") %>% 
  filter(!is.na(median)) %>% 
  right_join(select(data.R0, system_label, Temperature, Model, sigmaH, KH, median_R0 = median) %>%
               filter(KH %in% KH_vals & sigmaH %in% c(100, Inf))) %>%
  filter(median_R0 > 0) %>%
  group_by(system_ID) %>% 
  summarise(min_Temp = min(Temperature),
            max_Temp = max(Temperature))

val_lims <- tibble(sigmaH = c(100, Inf), 
                   min_median = c(-90, -0.05), 
                   max_median = c(5, 0.5))

dR0dk.df <- data.dR0dvar %>%
  filter(
    KH %in% KH_vals,
    sigmaH %in% c(100, Inf)
  ) %>%
  right_join(select(data.R0, system_label, Temperature, Model, sigmaH, KH, median_R0 = median) %>%
               filter(KH %in% KH_vals & sigmaH %in% c(100, Inf))) %>%
  right_join(temp_lims) %>% 
  group_by(system_ID) %>% 
  filter(Temperature > min_Temp, Temperature < max_Temp) %>% 
  ungroup() %>% 
  right_join(val_lims) %>% 
  group_by(sigmaH) %>% 
  filter(median > min_median, median < max_median) %>% 
  # filter(median_R0 > 0) %>%
  mutate(abs_median = abs(median)) %>%
  # filter(abs_median < 1e10) %>%
  mutate(sign_median = sign(median)) %>%
  filter(sign_median != 0, !is.na(sign_median)) %>%
  arrange(sign_median) %>%
  arrange(Temperature)

plot.dR0dk <- dR0dk.df %>%
  # filter(focal_var %in% c("Adult mortality rate")) %>%
  # Make a stacked plot, colored by parameter
  ggplot(aes(x = Temperature, y = median, color = focal_var, 
             # linetype = (as.factor(sign_median))
             )) +
  geom_line(lwd = 1) +
  scale_color_manual(
    name = "Focal trait:",
    values = rev(c(c4a("misc.okabe", 7), "black"))
  ) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(
    name = unname(TeX("Local sensitivity of $R_0$")),
    # limits = c(-1, 1),
    # limits = 10^c(-4, 4),
    # breaks = 10^(seq(-4, 4)),
    # labels = TeX(c("$10^{-4}$", "$10^{-3}$", "$10^{-2}$", "$10^{-1}$", "$10^0$", "$10^1$", "$10^2$", "$10^3$", "$10^4$")),
    # trans = "log10",
    expand = c(0, 0)
  ) +
  scale_linetype_manual(
    name = "Sign of sensitivity:",
    values = c(1, 3),
    breaks = c(1, -1),
    labels = c("Positive", "Negative")
  ) +
  facet_rep_grid(
    cols = vars(system_label),
    rows = vars(KH, sigmaH),
    labeller = labeller(
      system_label = sens_labels,
      sigmaH = as_labeller(appender_sigmaH, default = label_parsed),
      KH = as_labeller(appender_KH, default = label_parsed)
    ),
    scales = "free"
  ) +
  guides(linetype = guide_legend(
    title.position = "left",
    title.vjust = 0.5,
    direction = "vertical"
  )) +
  theme_minimal_hgrid(10) +
  theme(
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 8),
    legend.position = "bottom",
    legend.justification = 0.5,
    axis.title.x = element_text(hjust = 0.5),
    strip.text.x = ggtext::element_markdown(
      size = 10,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  )
